\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}

\title{Lead Delivery Procedure}
\author{Morgan Askins\thanks{UC Davis}}
\date{}

\begin{document}
\maketitle
\section*{Description}
Clean and transport 900 bricks totalling roughly 12 tons, split into 6 pallets, of lead from the fairport mine in Clevelend Ohio to SNOLab. The bricks will be washed and wrapped in plastic on the surface before being transported underground and stored in the SNOLab near the SNO+ detector. Bricks will be palletized prior to transport underground.
\section*{Identification of Hazards}
\begin{enumerate}
  \item Ingestion of lead dust
  \item Contamination of personnel
  \item Contamination of lab space
  \item Personal hazard of dropping lead bricks
\end{enumerate}
\section*{Mitigation of Hazards}
\begin{enumerate}
  \item When handling unwrapped bricks personel will wear filter masks, disposable Tyvek suits, safety glasses, and latex/nitrile gloves. 
  \item Bricks will be wrapped on the surface prior to being moved underground.
  \item Unwrapped bricks will only come into contact with plastic (disposable materials).
  \item Don't lift more than one brick at a time. Always wear steel-toed shoes while handling individual bricks.
\end{enumerate}
\newpage
\section*{Procedure}
\begin{enumerate}
  \item The lead will arrive on 6 pallets totalling 900 bricks (12 tons) which will be transfered via forklift to an above ground lab for cleaning on-site.
  \item Wearing all of the required clothing (Tyvek suit, safety glasses, filter masks, and disposable gloves), the bricks will be individually unpacked from the pallets to be cleaned.
  \item Cleaning will consist of using ethanol to scrub the surface of each brick for contaminents and wrapping the bricks in Saran wrap.
  \item Each brick will then be placed on a new clean pallet at 2 tons per pallet.
  \item Each pallet will then be wrapped in two layers of plastic before transport underground.
  \item The pallets will be individually transported underground to the SNOlab car wash.
  \item The first layer of plastic will be removed and disposed of and the pallets will be placed near the SNO+ detector until usage.
\end{enumerate}

\end{document}
